\vspace{-5.5ex} \bf Design Project 3: Dynamic Scheduling

### 2015-11-25 DP3/analysis/Report.tex
fixed some grammatical errors

\subsection{Out-of-Order Bandwidth}
With a larger RUU, a good next choice of parameter to alter was the bandwidths of the out-of-order units: the fetch queue size, decode width, issue width, and commit width. These values were increased from 4 to 8. While they could be increased separately, it did not seem to make much sense to have a fetch queue size or commit width that were different, for example, so for the sake of simplicity each value was altered as a group. The results are shown in Table 4. As with increasing the RUU size, changing these parameters yielded a modest improvement of 1.05x to IPC. This time, however, average and peak power increased by 43\% and 78\%, respectively. These numbers are still well within the typical range for a desktop CPU, so the increase in IPC is worth it.

@@

Designing an out-of-order processor is clearly much more involved than designing a simple in-order one. Each of the different parameters can affect each other significantly, and even after narrowing the design space considerably, there are still a huge amount of configurations available. Only a few such designs could be tested within the scope of this project, but they should be representative. As with most designs in computer architecture, the configurations in this project were full of trade-offs. If the target market were chosen differently, the best design would be markedly different from the one selected here. If a lower IPC were acceptable, the power consumption could be drastically lower. Likewise, if power consumption wasn't as much of a concern, more performance could have been squeezed out of the designs. OVerall, the final design strikes a good balance between performance and power consumption, which is excellent for the chosen market.

>>>>

\subsection{Out-of-Order Bandwidth}
With a larger RUU, a good next choice of parameter to alter was the bandwidths of the out-of-order units: the fetch queue size, decode width, issue width, and commit width. These values were increased from 4 to 8. While they could be increased separately, it did not seem to make much sense to do so. Thus for the sake of simplicity each value was altered as a group. The results are shown in Table 4. As with increasing the RUU size, changing these parameters yielded a modest improvement of 1.05x to IPC. This time, however, average and peak power increased by 43\% and 78\%, respectively. These numbers are still well within the typical range for a desktop CPU, so the increase in IPC is worth it.

@@

Designing an out-of-order processor is clearly much more involved than designing a simple in-order one. Each of the different parameters can affect each other significantly, and even after narrowing the design space considerably, there are still a huge amount of configurations available. Only a few such designs could be tested within the scope of this project, but they should be representative. As with most designs in computer architecture, the configurations in this project were full of trade-offs. If the target market were chosen differently, the best design would be markedly different from the one selected here. If a lower IPC were acceptable, the power consumption could be drastically lower. Likewise, if power consumption wasn't as much of a concern, more performance could have been squeezed out of the designs. Overall, the final design strikes a good balance between performance and power consumption, which is excellent for the chosen market.
